### 2019-08-27 paper/spad_single/sections/method.tex
Updated paper, realsense simulation complete, ordnet created.

\subsection{Monocular Depth Estimation}

\subsection{Global Depth Hints}

\begin{itemize}
	\item image formation model	
	\item training details
	\item simulations and comparison: qualitative and quantitative
\end{itemize}

>>>>

In this section, we describe the measurement model for a single-pixel
time-of-flight lidar sensor under diffuse, pulsed laser illumination. 
\subsection{Measurement Model}
Consider a laser which emits a pulse at time $t = 0$ with time-varying intensity
$g(t)$ uniformly illuminating some 3D scene. We parameterize the geometry of the
scene as a height map $z(x, y)$.
Neglecting albedo and falloff effects, an ideal detector counting photon events
from a location $(x,y)$ in the time interval $(n\Delta t, (n+1) \Delta t)$ would record

\begin{equation}
  \lambda_{x,y}[n] = \int_{n\Delta t}^{(n+1) \Delta t} (f * g)\paren*{t - 2z(x,y)/c} dt \label{single_loc_spad} 
\end{equation}

where $c$ is the speed of light, and $f$ is a function that models the temporal uncertainty in the
detector. Single-photon avalanche diodes (SPADs) are highly sensitive
photodetectors which are able to record single photon events with high temporal
precision \cite{Stuff}. Since the event corresponding to the detection of a
photon can be described with a Bernoulli random variable,
the total number of accumulated photons in this time interval follows a Poisson
distribution according to

\begin{equation}
  h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b} \label{global_hints}
\end{equation}

where $\alpha_{x,y} = r_{x,y}/z(x,y)^2$ captures the attenuation of the
photon counts due to the reflectance $r(x,y)$ of the scene and due to the
inverse square falloff $1/z(x,y)^2$.
In addition, $\eta$ is the detection probability of a photon
triggering a SPAD event, and $b = \eta a + d$ is the average number of background detections resulting
from ambient photons $a$
and erroneous ``dark count'' events $d$ resulting from noise within the SPAD.
% \newpage
% \begin{table*}[htbp]
%   \begin{center}
  %   \begin{tabularx}{\linewidth}{*{2}{X}}
  %     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/rgb.png} &
  %     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/rawdepth.png} \\
  %     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/depth_hist.png} &
  %     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/spad_hist.png} \\
  %   \end{tabularx}
  % \end{center}
  % \caption{Sample Image. Top Left is the RGB image. Top Right is ground truth
  %   depth. Bottom Left is Raw ground truth depth histogram. Bottom Right is
  %   simulated SPAD measurements. Notice how closer depths are magnified and far
  %   depths are attenuated.}
% \end{table*}

\subsection{Monocular depth estimation with global depth hints}
Given a single RGB image $I(x,y)$ and a vector of photon arrivals $h[n]$
described by equation \ref{global_hints}, we seek to
reconstruct the ground truth depth map $z(x,y)$.
Our method has two parts. First, we \textbf{initialize} our estimate of the depth map from the single RGB
image via a monocular depth estimator described below. Second, we \textbf{refine} this depth map using
the captured measurements $h[n]$ via exact histogram matching.

\paragraph{Initialization}
The first step in our method is to produce an initial estimate of ground truth
depth. Convolutional Neural Networks have been shown to produce accurate, if poorly-scaled, estimates of depth
from only a single image. We therefore choose to initialize our depth map
estimate $\hat z^{(0)}(x,y)$ using
a CNN. However, any depth estimator reliant on only a single
view may be used for this step. Furthermore, in the larger context of our
algorithm, it is more important that the network predict the correct ordinal
relationships between pixels - that is, to predict the correct relative ordering
of pixels $a$ and $b$, rather than to get all pixels exactly correct.

\paragraph{Exact Histogram Matching}
\begin{figure}
  \includegraphics[width=\textwidth/2]{sections/figures/full_pipeline/full_pipeline.jpeg}
  \caption{\textbf{Overview of the full pipeline} We use a CNN to get an initial
  per-pixel depth estimate. Then we perform exact histogram matching using
  intensity-weighted pixel values on the corrected SPAD data.}
\end{figure}
An image's \textit{histogram} is a pair of vectors $(h, b)$ where $h_i$ is the number of
pixels of the image whose value lies in the range $[b_i, b_i+1)$.
Then, given a source image $S$ with histogram $(h_s, b)$ and a target histogram
$(h_t, b)$, histogram matching generates a new image $M$ such that $h_m \approx
h_t$ and the pixel values in $M$ are in the same relative order as in $S$.
The full details of the exact histogram matching algorithm can be found in
\cite{Morovic2002}.

However, for our purposes, we need to modify our algorithm to accommodate
differing per-pixel weights. We can account for squared depth falloff

\paragraph{SPAD Denoising}
\begin{itemize}
  \item Talk about histogram matching in the ideal case, jump straight to intensity 
  \item Talk about histogram matching in our case, and how it approaches the
    ideal case. Discuss the following corrections 
    \begin{itemize}
      \item Ambient/DC - Use \cite{Xin2019} to justify looking for large edges,
        then the ambient estimate to get rid of the noise floor.
      \item Falloff
    \end{itemize}
  \item Talk about how the histogram matching works with intensity
    considerations applied, briefly.
  \item We don't address jitter or poisson noise.
\end{itemize}
\begin{equation}
  h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b} \label{global_hints}
\end{equation}
Given a SPAD with histogram $h$ according to the above equation, we first
process the SPAD to remove the effects of some of the terms. First, we 
\subsection{Implementation Details}
For the Monocular Depth Estimator, we use pretrained versions of the
the Deep Ordinal Regression Network (DORN) \cite{} and the DenseDepth Network.
The exact histogram matching method is as described in \cite{}.

### 2019-08-27 paper/spad_single/sections/related.tex
Paper update
Updated paper, realsense simulation complete, ordnet created.

\paragraph{Depth Imaging}

\begin{itemize}
	\item stereo and multiview
	\item structured illumination and random patterns (kinect, etc.), active stereo
	\item time of flight (continuous wave and pulsed)
	\item what we do: like pulsed but much simpler setup; no scanning, no spad array, ...
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Monocular Depth Estimation}

\begin{itemize}
	\item summary of architectures and cost functions: u-net type architecture with reverse huber loss
	\item what we do: same thing, but augment with global hints (inspired by these approaches, we do ...)
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Deep Sensor Fusion}

global hints for super-resolution, colorization, depth estimation 
%
\begin{itemize}
	\item colorization
	\item david's 2018 paper for depth estimation and denoising (see david's 2019 sig paper for related work)
	\item what we do: slightly different application
\end{itemize}

>>>>

% \paragraph{Depth Imaging}
% Include in intro, don't necessarily need it here.
% Conventional approaches to estimating depth from images include stereo-based
% approaches 
% \begin{itemize}
% 	\item stereo and multiview
% 	\item structured illumination and random patterns (kinect, etc.), active stereo
% 	\item time of flight (continuous wave and pulsed)
% 	\item what we do: like pulsed but much simpler setup; no scanning, no spad array, ...
% \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Monocular Depth Estimation}
Previous non-deep approaches used Markov Random Fields \cite{Saxena2006},
geometric approaches \cite{Hoiem2005}, and non-parametric, SIFT-based methods
\cite{Karsch2014}.
More recently, deep neural networks have been applied to the problem of estimating depth from a
single image. Eigen et. al. \cite{Eigen2014} use a multi-scale neural network to
predict depth at multiple scales. Godard et. al. \cite{Godard2017} use an
unsupervised approach (i.e. that does not require ground truth depth) that
trains a network using stereo pairs to produce disparity maps from
single images, which can then be used to recover the depth. Fu et. al.
\cite{Fu2018} combined a logarithmic depth discretization scheme with a novel
ordinal regression approach. Various experiments using different types of
encoder networks (e.g. ResNet, DenseNet) \cite{Laina2016} \cite{Alhashim2018}
have also been employed with some success, as have approaches mixing deep
learning with conditional random fields \cite{Xu2017}, and attention-based
approaches \cite{Xu2018} \cite{Hao2018}.

Despite achieving remarkable success on the monocular depth estimation task, none of these methods are able to
resolve inherent scale ambiguity in a principled manner (being monocular in nature). By combining a monocular
depth estimator with a depth histogram, our method is able to do so.

% \begin{itemize}
% 	\item summary of architectures and cost functions: u-net type architecture with reverse huber loss
% 	\item what we do: same thing, but augment with global hints (inspired by these approaches, we do ...)
% \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Depth Imaging and Sensor Fusion with SPADs}
Previous work (see \cite{Horaud2016} for a survey) has been able to use
single-pixel SPADs \cite{Lamb2010} and also 1D LinoSPADs in
tandem with various scanning or DMD devices to capture 3D volumes of photon arrivals
that can be used to reconstruct depth. Lindell et. al. \cite{Lindell2018} use a
LinoSPAD and epipolar scanline and fuse the SPAD data with an RGB image to
produce high-quality depth.  Our approach uses a single pixel SPAD but
does not require any scanning or DMD mechanism.

A parallel approach called 3D flash LiDAR uses a laser with an optical diffuser
as the illumination source and a 2D array of SPADs to capture the 3D volume
\cite{Stoppa2007, Niclass2005}. Such arrays are capable of reconstructing high
quality depth but remain relatively low resolution. Other arrays are able to
achieve higher resolution, but suffer from low fill factor \cite{Veerappan2011} or
sacrifice per-pixel TDC \cite{Zhang2018}.

Our approach uses flash LiDAR but requires only a single pixel 
sensor.
(Still need to flesh out this section more with some higher resolution SPAD arrays)
% \begin{itemize}
%   \item Scanned single-pixel and 1D arrays, but scanning is hard
%   \item high resolution arrays -> challenging to do TDC
%   \item Individual (non-scanning) SPADs already exist in e.g. iPhoneX, but use
%     is limited to proximity sensors.
%   \item What we do: No array (easier), no scanning (easier), much cheaper,
%     combined with RGB camera to do high-resolution depth imaging, a more complex
%     task.
% \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \paragraph{Deep Sensor Fusion}
% Maybe mention in previous section? 
% global hints for super-resolution, colorization, depth estimation 
%
% \begin{itemize}
	% \item colorization
	% \item david's 2018 paper for depth estimation and denoising (see david's 2019 sig paper for related work)
	% \item what we do: slightly different application
% \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Histogram Matching and Global Hints}
Histogram matching or histogram specification is a well-known image processing
technique \cite{Gonzalez2008} for adjusting an image so that it's histogram
matches some pre-specified histogram (often derived from another image).
Nikolova et. al. \cite{Nikolova2013} use optimization to recover a strict
ordering of the image pixels that allows an exact histogram match to be
obtained. Morovic et. al \cite{Morovic2002} provide a simple and concise method
that also achieves an exact histogram match while being very fast.
In the image reconstruction space, Swoboda and Schnörr \cite{Swoboda2013} use a
histogram to form an image prior based on the Wasserstein distance for image
denoising and inpainting. Rother et. al. \cite{Rother2006} use a histogram prior
to create an energy function that penalizes foreground segmentations with
dissimilar histograms. In a slightly different vein, Zhang et. al.
\cite{Zhang2017} train a neural network to produce realistically colorized
images given only a black-and-white image and a histogram of global color information.

Our method is essentially a modified form of the algorithm in
\cite{Morovic2002}, modified for our particular use case. Also worth noting is
the fact that most algorithms compute histograms from existing images, whereas
our method mesaures the depth histogram indirectly using photon arrivals.
%
% \begin{itemize}
%   \item Exact histogram matching paper used in this work
%   \item Wasserstein-based optimization techniques for
%     histogram-based regularization
% \end{itemize}
